Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-25 main_paper.tex
Minor changes to the Conclusion Section

This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in sharp regression discontinuity designs using a uniform
kernel. The approach proposed builds upon the developments and intuition
advanced by CCT and is based on a first-order bias correction. We exploit CCT's
theoretical insight through a new residual bootstrap. In particular, we propose
estimating the local linear model as usual, then estimating a local second order
polynomial and generating bootstrap datasets by resampling the residuals of that
polynomial. This bootstrap allows the bias of the linear model to be estimated
and removed, and the bootstrap can be repeated to accurately estimate the
sampling distribution of the bias-corrected estimator. These results demonstrate
that there are bootstrap procedures that can generate asymptotically valid
confidence intervals in the same settings as CCT's. The current implementation
of this bootstrap is very specialized, however, and relaxing its limitations
is the subject of ongoing research.

>>>>

This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in sharp regression discontinuity designs. The approach proposed builds upon the developments and intuition
advanced by CCT and is based on a first-order bias correction. We exploit CCT's
theoretical insight through a new wild bootstrap. In particular, we propose
estimating the local linear model as usual, then estimating a local second order
polynomial and generating bootstrap datasets based on that
polynomial. This bootstrap allows the bias of the linear model to be estimated
and removed, and the bootstrap can be repeated to accurately estimate the
sampling distribution of the bias-corrected estimator. These results demonstrate
that there are bootstrap procedures that can generate asymptotically valid
confidence intervals in the same settings as CCT's. The current implementation
of this bootstrap is somewhat specialized, however, and relaxing its limitations
is the subject of ongoing research.
